\documentclass{article}
\usepackage{setspace}
\usepackage[margin=1in]{geometry}

\title{Summary of ``Thermal Hall Effect Measurements using Strontium Titanate Microthermometers.''}
\author{Colin Tinsman}
\date{}

\begin{document}
\doublespacing
\maketitle
Thermal measurements are an important tool for studying new materials and identifying novel physics in condensed matter systems. In a sense, they are the most general experimental methods available to a condensed matter experimentalist: any excitation in a solid will carry energy, and thus heat. This makes them particularly applicable to studying systems with novel excitations that do not carry charge. Such measurements can be quite challenging to make, however. They require accurate and precise readings of the temperature at multiple points on a crystal, which are often quite small, only a few millimeters in any direction. These thermometers must be compatible with the cryogenic environment where the measurement takes place, and may also need to be compatible with intense magnetic fields.

This is especially important when making thermal Hall effect measurements: the thermal analogue of the Hall effect. This effect is often minute, rarely more than 1\% of the total thermal conductivity. It also often requires making measurements in magnetic fields of a few Tesla or more. These fields can interfere with standard methods of thermometry relying on resistive thermometers by way of their magnetoresistance. In order to eliminate the systematic issues with these devices, we have exploited the strongly temperature dependent dialectic permittivty of strontium titanate. This material is not itself a ferroelectric, but sits close to a quantum phase transition to a ferroelectric state. This causes its permittivity to increase rapidly until reaching a maximum a few Kelvin above absolute zero. By making small capacitors using this material as a dielectric, we can use this fact to measure temperature with great precision in a way that is not systematically affected by a magnetic field. This on its own opens up new possibilities for making thermal Hall effect measurements in strong magnetic fields, but since the permittivity saturates below a few Kelvin, the sensitivity of these devices rapidly degrades in this range. However, it has been noted that annealing strontium titanate in an oxygen-18 atmosphere can tune the properties of this material close to this quantum critical point, even making it ferroelectric if enough is incorporated. By moving strontium titanate close to this quantum phase transition without going over, the permittivity can be made to keep increasing down to temperatures below 1 Kelvin, where the mangetoresistance issues of conventional thermometers are most severe. 

In order to test these capacitive thermometers, thermal Hall effect measurements were carried out on bismuth. Bismuth is one of the best known semimetals, a material which hosts both electrons and holes, with a relatively low carrier density but high mobility. It is also well known for having ``Dirac-like'' bands, with carriers that have linear dispersion similar to a relativistic particle. These properties make it an important system for benchmarking new experimental techniques in condensed matter physics. Despite being an ``old material'', one which has been studied experimentally for over a century, thermal Hall effect measurements had only recently been performed on it up to 3 T. With the strontium titante microthermometers, we were able to conduct measurements up to 10 T and at temperatures down to 40 K. A large thermal Hall coefficient is measured in this system, indicative of high mobility carriers, and the overall field dependence displays behavior which is indicative of the presence of two carriers. The strontium titanate microthermometers allow us to continue to observe these properties in the intense magnetic field.

Another important application of these thermometry techniques is towards making measurements of frustrated magnets. These are systems where the geometry of the lattice interferes with magnetic ordering, resulting in a variety of new magnetic phases such as spin ices and quantum spin liquids. These systems have generated quite a bit of theoretical interest in the past decade, but they are difficult to study experimentally since they often have itinerant excitations which do not carry charge. This makes thermal transport measurements such as the thermal Hall effect all the more important for studying them. In this work we discuss our measurements on strontium copper borate, in which pairs of spin-1/2 sites are paired up in dimers with a ground state made up of a lattice of singlets. The magnetic excitations of this system are the mobile triplet states, called triplons. It has been predicted that these triplet bands could have non-trivial topology, making strontium copper borate a bosonic topological insulator, and resulting in a specific thermal Hall effect signal. Experimental measurements in this system fail to find this signal, casting doubt on this theory. However, we observe magnetic field dependent longitudinal thermal conductivity at temperatures below 1 K, where the triplet excitations should be frozen out. There may be some relation to another phenomena found in this material in this temperature range: the formation of spin superlattices, states where spins form ordered arrangements larger than the base unit cell of the material. 

\end{document}
